Brief notes on erosion

### 2020-08-26 docs/proposals/NSF/PostDocs/Subaward_Justification.tex
working on budget justification

I would like to request a restructuring of the NSF grant with Award
Number 2012560. PI Moore has left Florida State University (FSU) and
taken a faculty position at the US Naval Academy. Dr.~Moore's new
department does not have a graduate program, so the funded graduate
student's senior advisor will be co-PI Quaife at FSU. So that the grant
can be managed by FSU, I request that Dr.~Quaife becomes the lead PI and
Dr.~Moore becomes the co-PI, with a sub-contract created for the US Naval Academy that will manage Dr.~Moore's funding.

% I also request permission for FSU to create a sub-contract for the US Naval Academy that will manage Dr.~Moore's funding.

This request is written in consultation with Dr.~Moore. Please contact
me if further clarification is required.

>>>>

This letter serves as justification for a subaward of NSF grant Award
Number 2012560. Dr.~Moore at the US Naval Academy is uniquely qualified
to perform two deliverables:
\begin{enumerate}
  \item Characterizing permeability, anisotropy, and pore size dynamics
    to inform Darcy-based homogenized models.
  \item Developing and validating new parameterizations using machine
    learning techniques and numerical simulations.
\end{enumerate}
These efforts will be coordinate with PI Quaife throughout the duration
of the award, and they are fundamental to the success of the remaining
deliverables.

Please note that Dr.~Moore was originally a PI on this proposal, but it
was necessary to restructure his portion of the funding to a sub-award
as he left Florida State University.

This justification is written in consultation with Dr.~Moore. Please
contact me if further clarification is required.

### 2020-08-26 docs/proposals/NSF/budgets/budgetJustUSNA.tex
working on budget justification

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{C: Fringe Benefits}
The fringe benefits of co-PI Moore at USNA are 34\%. 
In addition a COLA of 3\% is added to estimate the cost of living increase government works may receive in January. \\
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    co-PI Moore Fringe & $\$3,259$ & $\$3,319$ & $\$3,392$ & $\$9,970$ \\
    \hline
    co-PI Moore COLA & $\$288$ & $\$293$ & $\$299$ & $\$880$ \\
    \hline
    Total & $\$3,546$ & $\$3,612$ & $\$3,692$ & $\$10,850$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{E: Domestic Travel}
%\hfill \\
%\noindent
The requested travel funds is to partially fund a domestic trip
for co-PI Moore in years 2 and 3.  The expected costs per
conference participant is $\$1,750$ with a breakdown of $\$600$ for
airfare, $\$750$ for lodging, $\$56$ for local transportation, $\$144$
for meals (four days at $\$36$ per day), and $\$200$ for conference
registration.  Potential meeting venues include several SIAM Meetings
(Annual Meetings, CSE, Dynamical Systems), APS Fluids Meetings, or
appropriately themed workshops. 
Alternatively, co-PI Moore may use these travel funds to visit PI Quaife and the funded graduate student at FSU in order to collaborate on the project.
Travel funds for the first year are removed due to the COVID crisis.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Domestic Travel &  & $\$1,000$ & $\$1,000$ & $\$2,000$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{G: Other Direct Costs}
%\noindent
\paragraph{\bf Materials and Supplies:} The requested materials and
supplies of \$1000 in year 1 is to partially fund a laptop or desktop computer for co-PI Moore. The computer will be used for developing the proposed algorithms and
presenting the results at conferences.
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{H: Total Direct Costs}
%\hfill \\
%\noindent
Total of Sections A--G.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$14,130.92$ & $\$14,374$ & $\$14,669$ & $\$43,174$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{I: Indirect Costs}
%\hfill \\
%\noindent
The US Naval Academy's indirect cost rate is
10\% for research on modified total direct costs (MTDC).
The base for overhead is $\$14,130.92$ in year 1, $\$14,374.31$ in
year 2, and $\$14,668.63$ in year 3.
The US Naval Academy defines a fiscal year to be July 1-June 30.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$1,413$ & $\$1,437$ & $\$1,467$ & $\$4,317$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{J: Total Direct and Indirect Costs}
%\hfill \\
%\noindent
Total of Sections H and I.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$15,544$ & $\$15,812$ & $\$16,135$ & $\$47,491$ \\
    \hline
  \end{tabular}
\end{center}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{C: Fringe Benefits}
The fringe benefits of co-PI Moore at USNA are 34\%. 
In addition a COLA of 3\% is added to estimate the cost of living increase government works may receive in January. \\
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    co-PI Moore Fringe & $\$3,259$ & $\$3,319$ & $\$3,392$ & $\$9,970$ \\
    \hline
    co-PI Moore COLA & $\$288$ & $\$293$ & $\$299$ & $\$880$ \\
    \hline
    Total & $\$3,547$ & $\$3,612$ & $\$3,691$ & $\$10,850$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{E: Domestic Travel}
%\hfill \\
%\noindent
The requested travel funds is to partially fund a domestic trip
for co-PI Moore in years 2 and 3.  The expected costs per
conference participant is $\$1,000$ with a breakdown of $\$300$ for
airfare, $\$300$ for lodging, $\$56$ for local transportation, $\$144$
for meals (four days at $\$36$ per day), and $\$200$ for conference
registration.  Potential meeting venues include several SIAM Meetings
(Annual Meetings, CSE, Dynamical Systems), APS Fluids Meetings, or
appropriately themed workshops.  Alternatively, co-PI Moore may use
these travel funds to visit PI Quaife and the funded graduate student at
FSU in order to collaborate on the project.  Travel funds for the first
year are removed due to the COVID crisis.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Domestic Travel &  & $\$1,000$ & $\$1,000$ & $\$2,000$ \\
    \hline
  \end{tabular}
\end{center}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection*{G: Other Direct Costs}
%%\noindent
%\paragraph{\bf Materials and Supplies:} The requested materials and
%supplies of $\$1000$ in year 1 is to partially fund a laptop or desktop
%computer for co-PI Moore. The computer will be used for developing the
%proposed algorithms and presenting the results at conferences.
%\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{H: Total Direct Costs}
%\hfill \\
%\noindent
Total of Sections A--G.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$13,132$ & $\$14,374$ & $\$14,668$ & $\$42,174$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{I: Indirect Costs}
%\hfill \\
%\noindent
The US Naval Academy's indirect cost rate is 10\% for research on
modified total direct costs (MTDC).  The base for overhead is
$\$13,132$ in year 1, $\$14,374$ in year 2, and $\$14,668$ in
year 3.  The US Naval Academy defines a fiscal year to be July 1-June
30.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$1,313$ & $\$1,437$ & $\$1,467$ & $\$4,217$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{J: Total Direct and Indirect Costs}
%\hfill \\
%\noindent
Total of Sections H and I.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$14,445$ & $\$15,811$ & $\$16,135$ & $\$46,391$ \\
    \hline
  \end{tabular}
\end{center}

### 2020-08-26 docs/proposals/NSF/budgets/budgetJustificationFSU.tex
working on budget justification

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{C: Fringe Benefits}
{\bf PI:} The fringe benefits of the PI are 17.06\%. \\
{\bf Ph.D.:} The fringe benefits of the graduate student are
0.1\% plus an $\$1,965$ health insurance. \\
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    PI & $\$1,800$ & $\$1,854$ & $\$955$ & $\$4,609$ \\
    \hline
    Ph.D. & $\$1,986$ & $\$1,987$ & $\$1,987$ & $\$5,960$ \\
    \hline
    Total & $\$3,786$ & $\$3,841$ & $\$2,942$ & $\$10,569$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{E: Domestic Travel}
%\hfill \\
%\noindent
The requested travel funds is to fund an annual domestic trip for the PI
or the Ph.D.~student.  The expected costs per conference participant is
$\$1,750$ with a breakdown of $\$600$ for airfare, $\$750$ for lodging,
$\$56$ for local transportation, $\$144$ for meals (four days at $\$36$
per day), and $\$200$ for conference registration.  Potential meeting
venues include several SIAM Meetings (Annual Meetings, CSE, Dynamical
Systems), APS Fluids Meetings, or appropriately themed workshops.  The
PI and Ph.D.~student will give presentations and actively participate in
the meeting or workshop.  Travel funds for the first year are removed
due to the COVID crisis
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Domestic Conferences &  & $\$1,750$ & $\$1,750$ & $\$3,500$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{G: Other Direct Costs}
%\noindent
\paragraph{\bf Materials and Supplies:} The requested materials and
supplies is to purchase one $\$1,500$ laptop with accessories, which is
not otherwise available, for the PI and Ph.D.~student in year 1.  The
laptop will be used for developing the proposed algorithms and
presenting the results at conferences. The laptop will give the group
members the flexibility to work on the proposed research remotely. The
laptop will be used exclusively for the proposed research. 
\\
\paragraph{\bf Other:} The requested other direct costs are to cover the
Ph.D.~student's tuition for 18 credit hours, at a rate of $\$407.55$ per
credit hour in year 1.  An annual increase of 1\% is included per
published university projections.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Materials and Supplies & $\$1,500$ & & & $\$1,500$ \\
    \hline
    Other & $\$7,336$ & $\$7,409$ & $\$7,484$ & $\$22,229$ \\
    \hline
    Total & $\$8,836$ & $\$7,409$ & $\$7,484$ & $\$23,729$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{H: Total Direct Costs}
%\hfill \\
%\noindent
Total of Sections A--G.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$44,175$ & $\$45,499$ & $\$40,053$ & $\$129,727$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{I: Indirect Costs}
%\hfill \\
%\noindent
Florida State University's federally negotiated indirect cost rate is
54\% for research on modified total direct costs (MTDC) which excludes
tuition. The base for overhead is $\$36,839$ in year 1, $\$38,090$ in
year 2, and $\$32,569$ in year 3. Florida State University defines a
fiscal year to be July 1--June 30.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$19,893$ & $\$20,569$ & $\$17,587$ & $\$58,049$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{J: Total Direct and Indirect Costs}
%\hfill \\
%\noindent
Total of Sections H and I.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$64,068$ & $\$66,068$ & $\$57,640$ & $\$187,776$ \\
    \hline
  \end{tabular}
\end{center}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{C: Fringe Benefits}
{\bf PI:} The fringe benefits of the PI are 18.54\%. \\
{\bf Ph.D.:} The fringe benefits of the graduate student are
0.6\% plus an $\$1,965$ health insurance. \\
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    PI & $\$1,956$ & $\$2,015$ & $\$1,037$ & $\$5,008$ \\
    \hline
    Ph.D. & $\$2,091$ & $\$2,095$ & $\$2,099$ & $\$6,285$ \\
    \hline
    Total & $\$4,047$ & $\$4,110$ & $\$3,136$ & $\$11,293$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{E: Domestic Travel}
%\hfill \\
%\noindent
The requested travel funds is to fund an annual domestic trip for the PI
or the Ph.D.~student.  The expected costs per conference participant is
$\$1,000$ with a breakdown of $\$300$ for airfare, $\$300$ for lodging,
$\$56$ for local transportation, $\$144$ for meals (four days at $\$36$
per day), and $\$200$ for conference registration. An additional $\$195$
is budgeted for year 2. Potential meeting venues include several SIAM
Meetings (Annual Meetings, CSE, Dynamical Systems), APS Fluids Meetings,
or appropriately themed workshops. The PI and Ph.D.~student will give
presentations and actively participate in the meeting or workshop.
Travel funds for the first year are removed due to the COVID crisis.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Domestic Conferences &  & $\$2,195$ & $\$2,000$ & $\$4,195$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{G: Other Direct Costs}
%\noindent
\paragraph{\bf Materials and Supplies:} The requested materials and
supplies is to purchase one $\$1,359$ laptop with accessories, which is
not otherwise available, for the PI and Ph.D.~student in year 1. The
laptop will be used for developing the proposed algorithms and
presenting the results at conferences. The laptop will give the group
members the flexibility to work on the proposed research remotely. The
laptop will be used exclusively for the proposed research. 
\\
\paragraph{\bf Subawards:} The requested subaward is for Dr.~Nick Moore
at the US Naval Academy to provide two of the deliverables as described
in the scope of work.
\\
\paragraph{\bf Other:} The requested other direct costs are to cover the
Ph.D.~student's tuition for 18 credit hours, at a rate of $\$407.55$ per
credit hour in year 1.  An annual increase of 1\% is included per
published university projections.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Materials and Supplies & $\$1,359$ & & & $\$1,359$ \\
    \hline
    Subawards & $\$14,445$ & $\$15,811$ & $\$16,135$ & $\$46,391$ \\
    \hline
    Other & $\$7,336$ & $\$7,410$ & $\$7,484$ & $\$22,230$ \\
    \hline
    Total & $\$23,140$ & $\$23,221$ & $\$23,619$ & $\$69,980$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{H: Total Direct Costs}
%\hfill \\
%\noindent
Total of Sections A--G.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$58,740$ & $\$62,025$ & $\$56,632$ & $\$177,397$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{I: Indirect Costs}
%\hfill \\
%\noindent
Florida State University's federally negotiated indirect cost rate is
54\% for research on modified total direct costs (MTDC) which excludes
tuition subaward costs after the first \$25,000. The base for overhead
is $\$51,504$ in year 1, $\$49,359$ in year 2, and $\$33,013$ in year 3.
Florida State University defines a fiscal year to be July 1--June 30.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$27,758$ & $\$26,654$ & $\$17,827$ & $\$72,239$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{J: Total Direct and Indirect Costs}
%\hfill \\
%\noindent
Total of Sections H and I.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$86,498$ & $\$88,679$ & $\$74,459$ & $\$249,636$ \\
    \hline
  \end{tabular}
\end{center}
